Poincar\'e--Friedrichs constants over triangulated domains

### 2024-05-01 draft.tex

\documentclass[a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{fullpage}
\input{header}

% Title, authors, and affiliations
\title{Poincar\'e--Friedrichs constants over triangulated domains}
\author{TCF, MWL, MV}

% Theorem environments

\begin{document}

\maketitle

\begin{abstract}
    We construct upper bounds for Poincar\'e--Friedrichs constants over triangulated domains. 
    These include the Poincar\'e, Maxwell, and Friedrichs constants as special cases. 
    The main application that we envision concern computable estimates over finite element patches. 
\end{abstract}

\section{Introduction}
\cite{ern2021finite}

% introductory paragraph

% Estimates for Poincare constants 
% \cite{bebendorf2003note}
% \cite{vohralik2005discrete}
% \cite{farwig2016note}
% Verfurth, Veeser & Verfurth 
% ...

% Estimates for Friedrichs constants (if any)

% Estimates for Maxwell constants (if any)

While it is known that finite element patches admit Poincar\'e--Friedrichs inequalities, 
we are not aware of computable estimates. 
Clearly, not all local patches describe convex subdomains. 
An ostensibly more practical class of domains are domains star-shaped with respect to a ball.
Indeed, finite element patches of Lipschitz satisfy that condition. 
Over patches around interior subsimplices, the size of interior ball only depends on the shape regularity of the triangulation. However, the interior ball can be arbitrarily small when the patch is around a boundary simplex at a reentrant corner, even if the mesh has good shape-regularity. 
Some interesting limit cases include the slit domain and the crossed bricks domain,
for which some finite element patches are not star-shaped with respect to any ball. 
\color{red}Our upper bounds do not depend on the angles of such reentrant corners, even in the aforementioned limit cases, but only the shape-regularity of the triangulation. \color{black}

It is often very helpful if a simplicial complex can be created recursively, starting with a single simplex. 
In particular, this enables the inductive method of proof.

Estimating Poincar\'e--Friedrichs over domains and manifolds with shellable triangulations is fundamentally restricted to spaces with the simplicial homology groups of discs and spheres. However, these estimates are important partial results. Forthcoming work will take these as a subcomponent in computing upper bounds for Poincar\'e--Friedrichs constants over simplicial triangulations of general $n$-dimensional manifolds. l

\section{Triangulations and polytopal shellings}

% 1. Develop some notation

We gather notions of simplicial meshes for the subsequent discussion.

A ${k}$-dimensional \emph{simplex} $T$ is the convex hull of ${k}+1$ affinely independent points $v_0, v_1, \ldots, v_{{k}} \in \mathbb{R}^{n}$. We call these the \emph{vertices} of the simplex $T$. 
If $S$ is a simplex whose vertices are also vertices of another simplex $T$, in which case $S \subseteq T$, 
then we call $S$ a subsimplex of $T$ and we call $T$ a supersimplex of $S$.

A family of simplices $\calT$ is a \emph{simplicial complex} or \emph{triangulation}, if its member simplices satisfy the following condition: 
(i) every subsimplex of any simplex in $\calT$ is itself part of $\calT$, and (ii) the intersection between any two simplices $T, T' \in \calT$ is either empty or a shared subsimplex of both $T$ and $T'$. 
The set of $k$-dimensional simplices in $\calT$ is denoted as $\subsimplex_{{k}}(\calT)$. 
We say that $\calT$ has dimension $n$ if it contains an $n$-dimensional simplex as a supersimplex for each simplex within it.

Given any simplex $T$, we write $\subsimplex(T)$ for the simplicial complex that contains all subsimplices of $T$. 
More specifically, $\subsimplex_{{k}}(T) \subseteq \subsimplex(T)$ denotes the set of $k$-dimensional subsimplices of $T$. 
Whenever $\calT$ is a simplicial complex and $T \in \calT$, we let $\supsimplex(\calT,T)$ be the set of simplices in $\calT$ that contain $T$.
We write $\supsimplex_{k}(\calT,T)$ for the set of $k$-dimensional simplices in $\supsimplex(\calT,T)$. 
Additionally, the notations $\Vertices(\calT) := \subsimplex_{0}(\calT)$ and $\Edges(\calT) := \subsimplex_{1}(\calT)$ refer to the vertices and edges of the simplicial complex, respectively. Similarly, if $\calT$ is an $n$-dimensional simplicial complex, we write $\Faces(\calT) := \subsimplex_{n-1}(\calT)$ for the faces of the triangulation.

When $\calT$ is a triangulation and $T \in \calT$, then $\calT(T)$ denotes the \emph{local patch} of $T$, which is the smallest simplicial subcomplex of $\calT$ that contains all supersimplices of $T$. Formally,
\begin{gather*}
    \calT(T) := \bigcup_{ T' \in \supsimplex(\calT,T) } \subsimplex(T').
\end{gather*}
A crucial observation is the following.

\begin{lemma}
 Let $\calT$ be an $n$-dimensional simplicial complex and let $T,T' \in \calT$.
 Then either $\calT_{n}(T) \cap \calT_{n}(T') = \emptyset$ or there exists $S \in \calT$
 such that $\calT_{n}(T) \cap \calT_{n}(T') = \calT_{n}(S)$ with $T, T' \subseteq S$.
\end{lemma}
\begin{proof}
 Let $F \in \calT$ be $n$-dimensional.
 We have $F \in \calT(T )$ if and only if all vertices of $T $ are vertices of $F$.
 We have $F \in \calT(T')$ if and only if all vertices of $T'$ are vertices of $F$.
 Consequently, $F \in \calT(T) \cap \calT(T)$ if and only if $F \in \calT(S)$,
 where $S \in \calT$ and $S$ is the convex closure of $F$ and $F'$.
\end{proof}

% 2. Develop manifold-like complexes and characterize them

An $n$-dimensional simplicial complex is called \emph{manifold-like} if for every $x \in \bigcup \calT$
we have one of the following two conditions:
\begin{itemize}
 \item 
 there exists $\epsilon > 0$ 
 and a homeomorphism 
 \begin{align*}
    \phi : \Ball_\epsilon(x) \cap \bigcup\calT  
    \rightarrow 
    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1 \right\}
 \end{align*}
 such that $\phi(x) = 0$,
 \item 
 there exists $\epsilon > 0$ and a homeomorphism 
 \begin{align*}
    \phi : \Ball_\epsilon(x) \cap \bigcup\calT 
    \rightarrow 
    \left\{ x \in \bbR^{n} \suchthat |x| \leq 1, x_n \leq 0 \right\}
 \end{align*}
 such that $\phi(x) = 0$.
\end{itemize}
This characterizes the union of the simplicial complex $\calT$ as a topological manifold with boundary.

We would like to have a purely combinatorial and computable criterion that characterizes manifold-like simplicial complexes. A first step in that direction is the following result.

\begin{lemma}\label{lemma:characterizationofmanifoldcomplexes}
    Let $\calT$ be an $n$-dimensional simplicial complex. The following are equivalent:
    \begin{itemize}
     \item $\calT$ is manifold-like
     \item $\calT(V)$ is the triangulation of a ball for all $V \in \Vertices(\calT)$
     \item $\calT(V)$ is manifold-like for all $V \in \Vertices(\calT)$
     \item $\calT(S)$ is the triangulation of a ball for all $S \in \calT$
     \item $\calT(S)$ is manifold-like for all $S \in \calT$
    \end{itemize}
\end{lemma}
\begin{proof}
    \color{red} TODO
\end{proof}

\begin{remark}
    Clearly, not every simplicial complex is the triangulation of some (embedded) topological manifold with or without boundary. 
    Conversely, for each dimension $n \geq 5$ there exists an $n$-dimensional compact topological manifold without a triangulation. % TODO: are these compact?
    % TODO There are computational limits to algorithmically deciding whether a simplicial complex represents a manifold. 
\end{remark}

% 3. Develop construction of complexes via adding patches

@@

It is a consequence of Lemma~\ref{lemma:characterizationofmanifoldcomplexes} that,
if $\calT$ is a manifold-like simplicial complex, then $\calT(S)$ is connected for all $S \in \calT$.
Moreover, a manifold-like simplicial complex $\calT$ is connected if and only if $\bigcup\calT$ is a connected topological space.

We let \emph{$k$-patching} refer to enumerations $S_1, S_2, \dots$ of $\subsimplex_{k}(\calT)$
such that for any $0 \leq m$, the union 
$\calU_{m} := \calT(S_0) \cup \calT(S_1) \cup \calT(S_2) \cup \dots \cup \calT(S_m)$
shares an $n$-simplex with the patch $\calT(S_{m+1})$.
We call the $k$-patching \emph{manifold-like} if $\calU_{m}$ is manifold-like for all $0 \leq m$.
Clearly, a $k$-patching only exists if $k < n$ and if $\calT$ is connected. 
We refer the reader to Figure~\ref{figure:illustrationpatching} for an illustration.

\begin{lemma}
    A connected manifold-like $n$-dimensional simplicial complex $\calT$ admits a $k$-patching for any $k < n$.
\end{lemma}
\begin{proof}
    We define an undirected graph by letting $\subsimplex_{k}(\calT)$ be the set of nodes 
    and connecting any $S, S' \in \subsimplex_{k}(\calT)$ if there exists $T \in \subsimplex_{k+1}(\calT)$ with $S, S' \subseteq T$. 
    Note that in this case $\calT(S) \cap \calT(S') = \calT(T)$. 
    Since $\calT$ is connected, the graph $\calG$ is connected.

@@

\begin{figure}
    \centering
    \begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
        \draw[dashed] (O) -- (A); \draw[dotted] (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}
    \begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw[dotted] (A) -- (B); \draw (B) -- (C) -- (D) -- (E) -- (F) -- (A);
        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}
    \begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw[dotted] (O) -- (C); \draw (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}
    \begin{tikzpicture}
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({cos(0)}, {sin(0)});
        \coordinate (B) at ({cos(60)}, {sin(60)});
        \coordinate (C) at ({cos(120)}, {sin(120)});
        \coordinate (D) at ({cos(180)}, {sin(180)});
        \coordinate (E) at ({cos(240)}, {sin(240)});
        \coordinate (F) at ({cos(300)}, {sin(300)});
        \fill[gray!20] (A) -- (B) -- (O) -- (F) -- cycle;
        \draw (A) -- (B) -- (C) -- (D) -- (E) -- (F) -- cycle;
        \draw[dashed] (O) -- (A); \draw (O) -- (B); \draw (O) -- (C); \draw[dotted] (O) -- (D); \draw (O) -- (E); \draw (O) -- (F);
    \end{tikzpicture}
    \caption{Examples and counterexamples for building a manifold-like $1$-patching of a $2$-dimensional manifold-like triangulation. (1) We have already added the edge patch along the dashed line and we add the edge patch along the dotted line. (2) The new edge patch already be a subset of the subtriangulation (3) An inadmissible choice because new edge patch has no overlap with current subtriangulation, though the next subtriangulation would be manifold-like (4) An inadmissible choice because new edge patch has no overlap with current subtriangulation and the next subtriangulation would not be manifold-like.}\label{figure:illustrationpatching}
\end{figure}

\begin{figure}
    \centering
    \begin{tikzpicture}[scale=0.5]
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({0.8*cos(  0)}, {0.8*sin(  0)});
        \coordinate (B) at ({0.8*cos(120)}, {0.8*sin(120)});
        \coordinate (C) at ({0.8*cos(240)}, {0.8*sin(240)});
        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
        \draw (A) -- (B) -- (C) -- cycle; \draw (X) -- (Y) -- (Z) -- cycle;
        \draw[fill=gray!20] (X) -- (Y) -- (B) -- cycle;
        \draw[fill=gray!20] (Y) -- (Z) -- (C) -- cycle;
        \draw[fill=gray!20] (Z) -- (X) -- (A) -- cycle;
        \draw[fill=gray!20] (A) -- (X) -- (B) -- cycle;
        \draw[fill=gray!20] (B) -- (Y) -- (C) -- cycle;
        \draw[fill=gray!20] (C) -- (Z) -- (A) -- cycle;
    \end{tikzpicture}
    \begin{tikzpicture}[scale=0.5]
        \coordinate (O) at (0, 0);
        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
        \draw (O) -- (A);
        \draw (O) -- (B);
        \draw (O) -- (C);
        \draw (O) -- (X);
        \draw (O) -- (Y);
        \draw (O) -- (Z);
        %
    \end{tikzpicture}
    \begin{tikzpicture}[scale=0.5] 
        \tikzset{z={(90:1cm)}, y={(-30:1cm)}, x={(210:1cm)}}
        % \tikzset{z={(90:1cm)}, y={(-10:1cm)}, x={(250:1cm)}}

        \coordinate (O) at (0, 0);
        \coordinate (A) at ({3.0*cos(  0)}, {3.0*sin(  0)});
        \coordinate (B) at ({3.0*cos(120)}, {3.0*sin(120)});
        \coordinate (C) at ({3.0*cos(240)}, {3.0*sin(240)});
        \coordinate (X) at ({3.0*cos( 60)}, {3.0*sin( 60)});
        \coordinate (Y) at ({3.0*cos(180)}, {3.0*sin(180)});
        \coordinate (Z) at ({3.0*cos(300)}, {3.0*sin(300)});
        \coordinate (T) at ({0}, {0}, {3});

        \draw[thick, fill=gray!30] (O) -- (C) -- (T) -- cycle;
        \draw[thick, fill=gray!30] (O) -- (Y) -- (T) -- cycle;
        \draw[thick, fill=gray!30] (O) -- (Z) -- (T) -- cycle;
        \draw[thick, fill=gray!30] (O) -- (A) -- (T) -- cycle;
        \draw[thick, fill=gray!30] (O) -- (B) -- (T) -- cycle;
        \draw[thick, fill=gray!30] (O) -- (X) -- (T) -- cycle;

    \end{tikzpicture}

    \caption{Example of a connected $2$-dimensional manifold-like simplicial complex, which triangulates an annulus, that does neither admit a manifold-like $0$-patching nor manifold-like $1$-patching.}\label{figure:annuluscounterexample}
\end{figure}

% \color{red}
% \begin{proposition}
%     Suppose that $\calT$ is a connected $n$-dimensional simplicial complex. Then the following are equivalent:
%     \begin{itemize}
%      \item $\calT$ is manifold-like
%      \item $\calT$ has a manifold-like $0$-patching
%      % \item There exists $1 \leq k \leq n$ such that $\calT$ has a $k$-patching
%     \end{itemize}
% \end{proposition}
% \color{black}

% 4. Shellability

We turn our attention to a different idea of how to incrementally construct a simplicial complex while maintaining well-behaved intermediate complexes. 
Given an $n$-dimensional simplicial complex $\calT$, a \emph{shelling} is an enumeration of the $n$-simplices $T_{0}, T_{1}, T_{2}, \dots \in \subsimplex_{n}(\calT)$ such that $( \calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m}) ) \cap \calT(T_{m+1})$ is a simplicial complex of dimension $n-1$. Notice that the last intersection is automatically a subcomplex of the boundary complex of the last simplex $T_{m}$, and is thus manifold like.

% \begin{lemma}
%     If an $n$-dimensional simplicial complex $\calT$ has a shelling $T_{0}, T_{1}, T_{2}, \dots$, then it is manifold-like.
%     In particular, $\calT(T_{0}) \cup \calT(T_{1}) \cup \dots \cup \calT(T_{m})$ is manifold-like for every $m \geq 0$.
% \end{lemma}
% \begin{proof}    
% \end{proof}

We notion of shelling is taken from Ziegler's book~\cite{}

% TODO: Ziegler, Lemma 8.7: if a complex has a shelling, then this gives a shelling of the stars

%

\section{Constructive estimate of $p$-Poincar\'e constants}

Let us assume that $p \in [1,\infty]$ and that $\Omega \subseteq \bbR^{n}$ is an open set. 
We say that a domain $\Omega \subseteq \bbR^{n}$ satisfies the Poincar\'e--Friedrichs inequality with exponent $p \in [1,\infty]$
if there exists a constant $C_{{\rm PF},\Omega,p} \geq 0$ such that the following holds:
for every vector field $\bff \in \nabla W^{1,p}(\Omega)$ there exists $u \in W^{1,p}(\Omega)$
such that $\nabla u = \bff$ and 
\begin{align}\label{math:inequalitypf:gradient}
    \| u \|_{L^{p}(\Omega)}
    \leq 
    C_{{\rm PF},\nabla,\Omega,p} 
    \| \bff \|_{L^{p}(\Omega)}
    .
\end{align}
We call $C_{{\rm PF},\Omega,p}$ the Poincar\'e--Friedrichs constant. 
This inequality implies an upper bound for the generalized inverse of the gradient operator $\nabla : W^{1,p}(\Omega) \rightarrow L^{p}(\Omega)^{n}$.

\begin{remark}
    Before we proceed, we wish to clarify the relationship between the Poincar\'e--Friedrichs inequality, in the sense introduced above, with other inequalities that are known are Poincar\'e inequality or also Friedrichs inequality in the literature.

    Given $p \in [1,\infty]$ and an open set $\Omega \subseteq \bbR^{n}$ of finite measure, 
    we say that $\Omega$ satisfies the Poincar\'e inequality with exponent $p$ 
    if there exists $C_{{\varnothing},\Omega,p} \geq 0$ such that 
    for all $u \in W^{1,p}(\Omega)$
    \begin{align}
        \| u - u_{\Omega} \|_{L^{p}(\Omega)}
        \leq 
        C_{\varnothing,\Omega,p} 
        \| \nabla u \|_{L^{p}(\Omega)}
        ,
    \end{align}
    where $u_{\Omega}$ is the \emph{average} of $u$ over $\Omega$, that is,
    \begin{align*}
        u_{\Omega} := |\Omega|^{-1} \int_{\Omega} u.
    \end{align*}
    Clearly, this Poincar\'e inequality implies the Poincar\'e--Friedrichs inequality and we have $C_{{\rm{PF}},\Omega,p} \leq C_{\varnothing,\Omega,p}$. 
    Towards a converse inequality, 
    let us first observe that the average of any $v \in W^{1,p}(\Omega)$ with $p < \infty$ satisfies the bound 
    \begin{align*}
        \| v_\Omega \|_{L^{p}(\Omega)}^{p}
        = 
        \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)| \right)^{p}
        \leq 
        \int_{\Omega} \left( |\Omega|^{-1} \int_{\Omega} |v(x)|^{p} \right)
        = 
        \| v \|_{L^{p}(\Omega)}^{p}
        .
    \end{align*}
    Here, we have used Jensen's inequality. 
    In the case $p = \infty$, any $v \in L^{\infty}(\Omega)$ satisfies $\| v_\Omega \|_{L^{\infty}(\Omega)} \leq \| v \|_{L^{\infty}(\Omega)}$. 
    We therefore combine 
    \begin{align*}
        \| v - v_\Omega \|_{L^{p}(\Omega)} 
        \leq
        2
        \| v \|_{L^{p}(\Omega)},
        \quad 
        v \in L^{p}(\Omega)
        .
    \end{align*}
    \begin{align*}
        \color{Emerald}
        \| u - u_\Omega \|_{L^{p}(\Omega)}^{p}
        \leq 
        2^{p-1} 
        \| u \|_{L^{p}(\Omega)}^{p}
        +
        2^{p-1} 
        \| u_\Omega \|_{L^{p}(\Omega)}^{p}
        \leq 
        2^{p} 
        \| u \|_{L^{p}(\Omega)}^{p}
        .
    \end{align*}
    We conclude that the Poincar\'e--Friedrichs inequality implies the Poincar\'e inequality with $C_{\varnothing,\Omega,p} \leq 2 C_{{\rm PF},\Omega,p}$. 
    In the special case $p=2$, we always have $\| u - u_\Omega \|_{L^{2}(\Omega)} \leq \| u \|_{L^{2}(\Omega)}$ for any $v \in L^{2}(\Omega)$,
    and therefore it even follows that $C_{\varnothing,\Omega,2} \leq C_{{\rm PF},\Omega,2}$. 
    \color{red} Question: can we modify the preceding discussion for general $p$ so that this special inequality for $p=2$ emerges as a limit case? Then we get stronger results for $p \approx 2$. Stern's paper? \color{black}

    The Poincar\'e--Friedrichs inequality, which we interpret as an upper bound for the operator norm of a generalized inverse of the gradient is more natural for our discussion because later sections will develop analogous inequalities for the curl and the divergence operators. 
    The kernel of those operators is infinite-dimensional, whereas the gradient only has a one-dimensional kernel. 
    When discussing Banach spaces, there is no canonical orthogonal projection on the kernel, unlike in the Hilbert space case, 
    which is why the Poincar\'e--Friedrichs inequality seems to be the more natural approach.
    \color{red} Make this last paragraph for concise.
\end{remark}

% either proceeding simplex by simplex, matching along faces 
% or proceeding patch by patch, matching over intersections
\begin{theorem}
    \color{red}Precise form of the inequality yet to be discussed, though the construction is clear.
\end{theorem}

\begin{proof}
 Let $u \in W^{1,p}(\Omega)$. 
 For each $F \in \calT$ of dimension $n-1$, 
 we let $u_F \in W^{1,p}(U_F)$ such that $\nabla u_F = \nabla u$ over $U_F$ and such that $\| u_F \|_{L^{p}(U_F)} \leq C_{{\rm{P}},F} \| \nabla u_F \|_{L^{p}(U_F)}$.

 Since $\calT$ is strongly connected, there exists an enumeration of $n$-simplices $T_0, T_1, \dots, T_M$ such that for any $1 \leq m \leq M$ there exists some fixed but arbitrary $0 \leq j < m$ such that $F_m := T_m \cap T_j$ is a face of dimension $n-1$. We write $\Omega_m := \cup_{j=0}^{m} T_m$. Hence $\Omega = \Omega_M$.

%  We let $T \in \calT$ be the first $n$-simplex. 
%  There exists We already have

 Suppose that $1 \leq m \leq M$ such that there exists $w_{m-1} \in W^{1,p}(\Omega_{m-1})$ with $\nabla w_{m-1} = \nabla u$ over $\Omega_m$. Hence $c_{\star} := w_{m-1} - u_{|\Omega_{m-1}}$ is a constant. 
 By assumption, $T_{m}$ shares the face $F_{m}$ with $T_{j}$. 
 Since $\nabla u_{F_{m}|T_j} = \nabla w_{m-1|T_j}$,
 there exists a constant $c_{m} := w_{m-1|T_j} - u_{F_{m}|T_j}$.
 We define $u'_{F_m} := u_{F_m} + c_{m} \in W^{1,p}(U_F)$.
 By construction, $\nabla u'_{F_m} = \nabla u_{F_m} = \nabla u_{|U_{F_m}}$ and $u_{F_{m}|T_j} = w_{m-1|T_j}$. 
 But that already implies $u'_{F_m} = u_{|F_m} - c_{\star}$. 
 As we define a measurable function $u'_{\star} \in W^{1,p}(\Omega_m)$ by extending $w_{m-1}$ with $u'_{F_m|T_m}$.
 Moreover, 
 \begin{gather*}
    \| u'_{F_m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \| c_{m} \|_{L^{p}(T_m)},
    \qquad 
    \| c_{m} \|_{L^{p}(T_m)}
    \leq 
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| c_{m} \|_{L^{p}(T_j)},
    \\ 
    \| c_{m} \|_{L^{p}(T_j)}
    \leq 
    \| w_{m-1}\|_{L^{p}(T_j)} + \| u_{F_{m}} \|_{L^{p}(T_j)} 
    .
 \end{gather*}
 In particular,
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}
    \leq 
    \| u_{F_m} \|_{L^{p}(T_m)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| u_{F_{m}} \|_{L^{p}(T_j)}
    +
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_j)}
    .
 \end{align*}
 In the special case $p < \infty$, we also find 
 \begin{align*}
    \| w_{m} \|_{L^{p}(T_m)}^{p}
    &\leq 
    3^{p-1}
    \| u_{F_m} \|_{L^{p}(T_m)}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_j) }
    \| u_{F_{m}} \|_{L^{p}(T_j)}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m)^{\frac 1 p} }{ \vol(T_j)^{\frac 1 p} }
    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
    \\&\leq 
    3^{p-1}
    \max\left( 1, \frac{ \vol(T_m) }{ \vol(T_j) } \right)
    \| u_{F_m} \|_{L^{p}(U_{F_m})}^{p}
    +
    3^{p-1}
    \frac{ \vol(T_m) }{ \vol(T_j) }
    \| w_{m-1}\|_{L^{p}(T_j)}^{p}
    .
 \end{align*}
 Recursive application provides the desired result. 
\end{proof}

\begin{remark}
    The previous result depends on only a few parameters of the triangulation:
    the length of any traversal from the root simplex,
    the ratios of the volumes of adjacent simplices,
    the Poincar\'e constants on each face patch, and the Poincar\'e constant of the initial simplex. 
    The aforementioned local Poincar\'e constants can generally be estimated in terms of shape-parameters. 
    If the face patches of the triangulation are convex, then better estimates are possible. 
\end{remark}

\section{Constructive estimate of $p$-Poincar\'e--Friedrichs constants}
% Repeat for H(curl), H(div), and differential forms

\section*{Acknowledgments}

\begin{remark}
    Suppose that $\calT$ is a simplicial complex and that $T$ is a simplex, $T \notin \calT$, such that $\calS := T \cap |\calT|$ is a subcomplex of $\partial T$. 
    According to the simplicial Mayer-Vietoris theorem, there exists an exact sequence 
    \begin{align*}
        \begin{CD}
            \dots \longrightarrow H_{k}(\calS) \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow H_{k-1}(\calS) \longrightarrow\dots 
        \end{CD}
    \end{align*}
    We notice that $\calS$, $\calT$, $T$ and $\calT \cup T$ are each connected, and hence their zeroth homology groups are isomorphic to $\bbZ$. 
    By the nature of the mappings in the Mayer-Vietoris sequence, we see that 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
    is an exact sequence. 
    Moreover, $H_{k}(\calS) = H_{k}(T) 0$ for $0 < k < n-1$. Hence, for $1 < k < n-1$,
    the Mayer-Vietoris sequence includes the exact sequence 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{k}(\calT \oplus T) \longrightarrow H_{k}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
    and we conclude that $H_{k}(\calT) = 0$ for $1 \leq k \leq n-1$.
    Finally, the Mayer-Vietoris sequence includes the exact sequences 
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{n}(\calT \oplus T) \longrightarrow H_{n}(\calT \cup T) \longrightarrow H_{n-1}(\calS) \longrightarrow H_{n-1}(\calT \oplus T) \longrightarrow H_{n-1}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
    Here, if $n=1$, it already follows that $H_{n}(\calT \oplus T) \simeq H_{n}(\calT \cup T)$.
    % We know that  $H_{0}(\calT \cup T) \simeq H_{0}(\calT) \simeq H_{0}(T) \simeq H_{0}(\calS) \simeq \bbZ$ because the respective simplicial complexes are path-connected. 
    % Hence $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
    % one easily sees that $H_{0}(\calT \cup T) \simeq \bbZ$ and $H_{1}(\calT) \oplus H_{1}(T) \simeq H_{1}(\calT \cup T)$. 
    If $\calS$ is isomorphic to disk,
    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
    If instead $\calS$ is isomorphic to a sphere, 
    then $H_{n}(\calT \cup T) \simeq H_{n}(\calT \oplus T)$ and $H_{n-1}(\calT \cup T) \simeq H_{n-1}(\calT \oplus T)$ follow immediately.
    % Moreover, Thus $H_{n}(\calT \cup T) = H_{n}(\calT) \oplus H_{n}(\calS)$.
    % We conclude that any shellable simplicial complex has the homology groups of a disk or a sphere. 
    % NB: the zeroth homology is always free, and the n-th homology group, being the kernel of a mapping free abelian group, is free as well.
    \begin{align*}
        \begin{CD}
            0 \longrightarrow H_{1}(\calT) \oplus H_{1}(T) \longrightarrow H_{1}(\calT \cup T) \longrightarrow H_{0}(\calS) \longrightarrow H_{0}(\calT) \oplus H_{0}(T) \longrightarrow H_{0}(\calT \cup T) \longrightarrow 0 
        \end{CD}
    \end{align*}
\end{remark}

A simplicial $n$-dimensional complex $\calT$ is called shellable if its $n$-simplices can be arranged in linear order $T_0, T_1, \dots$ in such a way that the subcomplex $( \cup_{i=0}^{k-1} T_i ) \cap T_k$ has dimension $n-1$ for all $k > 0$.

\bibliographystyle{plain}
\bibliography{library}

\end{document}

>>>>

% Develop construction of complexes via adding patches 
\subsection{Patch coverings}

@@

It is a consequence of Lemma~\ref{lemma:characterizationofmanifoldcomplexes} that,
if $\calT$ is a manifold-like simplicial complex, then $\patch_{\calT}(S)$ is connected for all $S \in \calT$.
Moreover, a manifold-like simplicial complex $\calT$ is connected if and only if $\bigcup\calT$ is a connected topological space.

We let \emph{$k$-patching} refer to enumerations $S_1, S_2, \dots$ of $\subsimplex_{k}(\calT)$
such that for any $0 \leq m$, the union 
$\calU_{m} := \patch_{\calT}(S_0) \cup \patch_{\calT}(S_1) \cup \patch_{\calT}(S_2) \cup \dots \cup \patch_{\calT}(S_m)$
shares an $n$-simplex with the patch $\patch_{\calT}(S_{m+1})$.
We call the $k$-patching \emph{manifold-like} if $\calU_{m}$ is manifold-like for all $0 \leq m$.
Clearly, a $k$-patching only exists if $k < n$ and if $\calT$ is connected. 
We refer the reader to Figure~\ref{figure:illustrationpatching} for an illustration.

\begin{lemma}
    A connected manifold-like $n$-dimensional simplicial complex $\calT$ admits a $k$-patching for any $k < n$.
\end{lemma}
\begin{proof}
    We define an undirected graph by letting $\subsimplex_{k}(\calT)$ be the set of nodes 
    and connecting any $S, S' \in \subsimplex_{k}(\calT)$ if there exists $T \in \subsimplex_{k+1}(\calT)$ with $S, S' \subseteq T$. 
    Note that in this case $\patch_{\calT}(S) \cap \patch_{\calT}(S') = \patch_{\calT}(T)$. 
    Since $\calT$ is connected, the graph $\calG$ is connected.

@@
